Static Analysis by Path Focusing

### 2011-04-21 report/report.tex
fix compilation problem in the analyzer + update of the report

\def\R{\mathbb{R}}
\def\Z{\mathbb{Z}}
\def\N{\mathbb{N}}
\def\Q{\mathbb{Q}}
\def\P{\mathcal{P}}

@@

@@

\begin{enumerate}
\item Each numerical SSA variable of the control flow graph has its definition
in the $\rho$ formula.
\item For each operation in the program, we encode its semantic, expressed in
terms of the boolean and numerical SSA variables. For instance, if the CFG
contains the affectation $x.2 = x.1 + 1$, then we simply add $x.2 = x.1 + 1$ in
the formula.
\item For each transition $(p_i,p_j) \in E$, we set $t_{i,j} = c(i,j)$, where
$c(i,j)$ express the condition that needs to be true to go through the
transition. For instance, $c(i,j)$ could be of the form $x < y$, \dots
If the transition is undeterministic, then $c(i,j) = c_{i,j}$, where
$c_{i,j}$ is a boolean variable left undeterministic.
\item For each point $p_i \notin P_R$, we set the reachability predicate 
$b_i = \displaystyle \bigvee_{(p_j,p_i)\in E} t_{i,j}$.
\item For each point $p_i^d \in P_R$, we set the reachability predicate 
$b_i^d = \displaystyle \bigvee_{(p_j,p_i)\in E} t_{i,j}$. 
\item $\Phi$-variables are treated differently, depending on the control point
$p$ where they are defined. To be completed !!

\end{enumerate}

@@

(b) control flow graph (a), such as it is represented by the SMT formula $\rho$.
Points in $P_R$ have been split into a ``source'' point and a ``destination''
point, and $\Phi$-variables associated to points in $P_R$ have been primed.
\end{minipage} 
\caption{}
\end{figure}

>>>>

\def\R{\mathbb{R}}
\def\Z{\mathbb{Z}}
\def\N{\mathbb{N}}
\def\Q{\mathbb{Q}}
\def\P{\mathcal{P}}
\def\ite{\textnormal{ite\ }}

@@

To Be Completed

@@

\begin{enumerate}
\item Each numerical SSA variable of the control flow graph has its definition
in the $\rho$ formula.
\item For each operation in the program, we encode its semantic, expressed in
terms of the boolean and numerical SSA variables. For instance, if the CFG
contains the affectation $x.2 = x.1 + 1$, then we simply add $x.2 = x.1 + 1$ in
the formula. This equality expression is noted $assign(x.2)$. 
$assign(x)$ is defined for each numerical SSA-variable of the program.
\item For each transition $(p_i,p_j) \in E$, we set $t_{i,j} = B_i\ \wedge \
c(i,j)$, where $B_i = b_i^s$ if $p_i \in P_R$, or $b_i$ if not.
$c(i,j)$ express the condition that needs to be true to go through the
transition. For instance, $c(i,j)$ could be of the form $x < y$, \dots
If the transition is undeterministic, then $c(i,j) = c_{i,j}$, where
$c_{i,j}$ is a boolean variable left undeterministic.
\item For each point $p_i \notin P_R$, we set the reachability predicate 
$b_i = \displaystyle \bigvee_{(p_j,p_i)\in E} t_{j,i}$.
\item For each point $p_i^d \in P_R$, we set the reachability predicate 
$b_i^d = \displaystyle \bigvee_{(p_j,p_i)\in E} t_{j,i}$. 
\item Numerical $\Phi$-variables assignations have to be expressed in the $\rho$
formula. We simply use $\ite$ (\emph{if-then-else}) statements, standardly defined in the
SMT-Lib format \cite{BarST-SMTLIB}, for giving the right value to the variable,
depending on the incoming transition we come from. Generally, for a
$Phi$-variable $x = \Phi(x_1,x_2,\dots,x_n)$ in control point $p_i$ with the
ordered incoming transitions $t_{j_1,i},t_{j_2,i},\dots,t_{j_n,i}$, we set:

$$x = \ite (t_{j_1,i})\  (x_1)\  (\ite (t_{j_2,i})\  (x_2)\  (\ite\  \dots))$$

where $\ite (c)\ (x)\ (y)$ is equal to $x$ if $c = true$, else $y$.

If the point where the $\Phi$-variable $x$ is defined is in
$P_R$, one need to rename $x$ into $x'$:
\begin{itemize}
\item $x$ will be the value of $x$ at the beginning of the path.
\item $x'$ will be the value of $x$ at the end of the path.
\end{itemize}
Indeed, there can be uses of $x$ along the path, and these uses refer to the
old value of $x$. 
\end{enumerate}

Finally, the $\rho$ formula is the following:

\begin{eqnarray*}
\rho = & \displaystyle\bigwedge_{p_i \notin P_R}& \left[ (b_i = \bigvee_{(p_h,p_i) \in E}
t_{h,i}) \wedge ( \bigwedge_{(p_i,p_j)\in E} t_{i,j} = b_i \wedge c(i,j))
\right] \wedge \\
 & \displaystyle\bigwedge_{p_i \in P_R}& \left[ (b_i^d = \bigvee_{(p_h,p_i) \in E}
 t_{h,i}) \wedge ( \bigwedge_{(p_i,p_j)\in E} t_{i,j} = b_i^s \wedge
 c(i,j)) \right] \wedge \\
 & \displaystyle\bigwedge_{x \in \Sigma}& assign(x)
\end{eqnarray*}

where $\Sigma$ is the set of the numerical SSA-variables of the program.

@@

(b) control flow graph (a), such as it is represented by the SMT formula $\rho$.
Points in $P_R$ have been split into a ``source'' point and a ``destination''
point, and $\Phi$-variables associated to points in $P_R$ have been primed.
\end{minipage} 
\caption{Example (cont'd)}
\end{figure}
